Neural Connectome of the Ctenophore Statocyst

### 2025-04-09 manuscript/Manuscript.qmd
edit correlation analysis

---
title: "Neural Connectome of the Ctenophore Statocyst"
subtitle: |
  **Kei Jokura**$^{1,2,3,4*}$, **Sanja Jasek**$^{1,2,6}$, **Lara Kewalow**$^{6}$, **Pawel Burkhardt**$^{5}$, **Gáspár Jékely**$^{1,2,6,*}$  
  <br><br>  
  $^{1}$ Living Systems Institute, University of Exeter, Exeter, EX4 4QD, United Kingdom  
  <br>
  $^{2}$ Biosciences, Faculty of Health and Life Sciences, University of Exeter, Exeter EX4 4QD, UK
  <br>
  $^{3}$ Exploratory Research Center on Life and Living Systems (ExCELLS), Okazaki, 444-8787, Japan  
  <br>  
  $^{4}$ National Institute for Basic Biology (NIBB), Okazaki, 444-8585, Japan  
  <br>  
  $^{5}$ Michael Sars Centre, University of Bergen, Norway  
  <br>
  $^{6}$ Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany  <br><br>  
  **$^{*}$ Correspondence:**  
  [jokura@nibb.ac.jp](mailto:jokura@nibb.ac.jp),  
  [gaspar.jekely@cos.uni-heidelberg.de](mailto:gaspar.jekely@cos.uni-heidelberg.de)
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
max-width: 100%
format:
  html:
    embed-resources: true 
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

@@

This work was funded by ... JSPS... This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 101020792).

>>>>

---
title: "Neural Connectome of the Ctenophore Statocyst"
subtitle: |
  **Kei Jokura**$^{1,2,3,4,5*}$, **Sanja Jasek**$^{1,2,6}$, **Lara Kewalow**$^{6}$, **Pawel Burkhardt**$^{7}$, **Gáspár Jékely**$^{1,2,6,*}$  
  <br><br>  
  $^{1}$ Living Systems Institute, University of Exeter, Exeter, EX4 4QD, United Kingdom  
  <br>
  $^{2}$ Biosciences, Faculty of Health and Life Sciences, University of Exeter, Exeter EX4 4QD, UK
  <br>  
  $^{3}$ Grass Laboratory, Marine Biological Laboratory, Woods Hole, MA 02543, USA  
  <br> 
  $^{4}$ Exploratory Research Center on Life and Living Systems (ExCELLS), Okazaki, 444-8787, Japan  
  <br>  
  $^{5}$ National Institute for Basic Biology (NIBB), Okazaki, 444-8585, Japan  
  <br> 
  $^{6}$ Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany  
  <br>
  $^{7}$ Michael Sars Centre, University of Bergen, Norway
  <br><br>  
  **$^{*}$ Correspondence:**  
  [jokura@nibb.ac.jp](mailto:jokura@nibb.ac.jp),  
  [gaspar.jekely@cos.uni-heidelberg.de](mailto:gaspar.jekely@cos.uni-heidelberg.de)
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
max-width: 100%
format:
  html:
    embed-resources: true 
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

@@

This work was supported by the Japan Society for the Promotion of Science (JSPS) Overseas Research Fellowships, the Grass Foundation, the Kavli Foundation, and the Marine Biological Laboratory (MBL). This project also received funding from the European Research Council (ERC) under the European Union’s Horizon 2020 research and innovation programme (grant agreement No. 101020792). We thank Dr. Réza Shahidi for sectioning and imaging, and Paulina Cherek for high-pressure freezing and sample preparation. We are also grateful to Dr. Chris Bjornsson, the MBL Central Microscopy Facility, Dr. Shoji A. Baba, and Dr. Kogiku Shiba (Shimoda Marine Research Center) for their assistance with microscopy.
